Supporting Information

### 2021-09-03 vertical-thermal-review_SI.Rmd
knit in latest NEON table, some cleanup

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
NEON_table <- read.csv("NEON_height_profiles/NEON_sites_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
NEON_table <- NEON_table[c(1:6)] #select and order columns for inclusion
ft <- flextable(NEON_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .7)
ft <- width(ft, 2, width = .75)
ft <- width(ft, 3, width = 1.5)
ft <- width(ft, 4, width = .5)
ft <- width(ft, 5, width = 1)
ft <- width(ft, 6, width = 1.5)
ft
```

@@

# `r SIfig_NEON_all_legend`
![**Figure `r SIfig_NEON_all`. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in July mean ± 1 standard deviation for maximum photosyntehtically active ratiation (PAR), maximum wind speed, minimum humidity, maximum $T_{air}$, and maximum biological temperature, $T_{bio}$. Sites are grouped into the following categories: (A) (sub)subtropical and warm temperate broadleaf: ..., (B) temperate open/ savanna forests: ..., (C) temperate mesic broadleaf forests: ..., (D) temperate conifer forests: ..., (E) northern and boreal forests: ...  [Issue #35](https://github.com/EcoClimLab/vertical-thermal-review/issues/35). ](NEON_height_profiles/figures/profile_all_groups.png)

## References

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
NEON_table <- read.csv("NEON_height_profiles/NEON_sites_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
NEON_table <- NEON_table[c(2:6)] #select and order columns for inclusion
ft <- flextable(NEON_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .75)
ft <- width(ft, 2, width = 2)
ft <- width(ft, 3, width = .5)
ft <- width(ft, 4, width = 1.2)
ft <- width(ft, 5, width = 2)
ft
```

@@

# `r SIfig_NEON_all_legend`
![**Figure `r SIfig_NEON_all`. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in July mean ± 1 standard deviation for maximum photosyntehtically active ratiation (PAR), maximum wind speed, minimum humidity, maximum $T_{air}$, and maximum biological temperature, $T_{bio}$. Site information is given in Supporting Information Table `r NEON_sites`, and analysis details in Supporting Information Methods `r appendix_NEON_methods`.](NEON_height_profiles/figures/profile_all_groups.png)

\newpage
## References
